### 2023-10-20 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions

Another difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. The bottom of
Figure~\ref{fig:lubricationComposite} shows the 
\textcolor{blue}{
tangential
}
%tank-treading
velocities of four Lagrangian points. The inset shows the vesicle
configuration in the closely-fitting part of the channel, the black
dashed line is the center line of the channel, the marks are the four
Lagrangian points, and the rounded arrow denotes the direction of
rotation. 
\textcolor{blue}
{
To determine if a vesicle is tank-treading, we first calculate the
average, maximum, and minimum tangential velocities over all $N$
Lagrangian points when the vesicle's center of mass is in the interval
$[4,10]$. If the maximum and minimum tangential velocities are within
15\% of the average tangential velocity, we characterize the vesicle as
tank-treading. The average tangential velocities are $-1.00 \times
10^{-1}$ for the stiff single-component vesicle, $3.31 \times 10^{-2}$
for the floppy single-component vesicle, and $-8.48 \times 10^{-1}$ for
the multicomponent vesicle. The spread of the maximum and minimum
velocities from these average tangential velocities are $1.2\%$ for the
stiff single-component vesicle, $12\%$ for the multicomponent vesicle,
and over $300\%$ for the floppy single-component vesicle. Therefore, we
classify the stiff single-component and multicomponent vesicles as tank
treading, while the floppy single-component is not tank treading.
}
%The stiff single-component and multicomponent vesicles are
%clearly tank treading.
The direction and speed of the tank-treading depends on how much of the
vesicle membrane is exposed to positive shear (below the center line)
versus how much is exposed to negative shear (above the center
line)~\cite{kao-bir-mis2009}. The majority of the membrane of the stiff
single-component and multicomponent vesicles are below the center line,
and this results in a clockwise tank-treading behavior. In contrast, the
majority of the membrane of the floppy single-component vesicle is above
the center line, and the result is counterclockwise 
\textcolor{blue}{
rotation, but, again, the vesicle dynamics are not tank-treading as the
vesicle is undergoing large normal deformations.
}
%tank-treading. 
\textcolor{blue}{
Finally, the stiff single-component vesicle tank treads faster than the
multicomponent cases since more of its membrane is located below the
center line.
}
%In addition, the tank-treading velocity can be correlated to the
%percentage of its membrane that is below the center line. 
%We note, however, that the floppy single-component vesicle is still
%undergoing deformations, so the tangential velocities have not converged
%to a fixed value.

>>>>

Another difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. 
%The bottom of Figure~\ref{fig:lubricationComposite} shows the
%tank-treading velocities of four Lagrangian points. The inset shows the
%vesicle configuration in the closely-fitting part of the channel, the
%black dashed line is the center line of the channel, the marks are the
%four Lagrangian points, and the rounded arrow denotes the direction of
%rotation. 
\textcolor{blue}
{
To determine if a vesicle is tank-treading, we first calculate the
average, maximum, and minimum tangential velocities over all $N$
Lagrangian points when the vesicle's center of mass is in the interval
$[4,10]$. If the difference of the maximum and minimum tangential
velocities is within 15\% of the average tangential velocity, we
characterize the vesicle as tank-treading. These relative relative
spreads are plotted in the bottom row of
Figure~\ref{fig:lubricationComposite}. The average tangential velocities
are $-1.00 \times 10^{-1}$ for the stiff single-component vesicle, $3.31
\times 10^{-2}$ for the floppy single-component vesicle, and $-8.48
\times 10^{-1}$ for the multicomponent vesicle. The difference of the
maximum and minimum velocities relative to the average tangential
velocities is $1.2\%$ for the stiff single-component vesicle, $12\%$ for
the multicomponent vesicle, and over $300\%$ for the floppy
single-component vesicle. Therefore, we classify the stiff
single-component and multicomponent vesicles as tank treading, while the
floppy single-component is not tank treading.}
%The stiff single-component and multicomponent vesicles are
%clearly tank treading.
The direction and speed of the tank-treading depends on how much of the
vesicle membrane is exposed to positive shear (below the center line)
versus how much is exposed to negative shear (above the center
line)~\cite{kao-bir-mis2009}. The majority of the membrane of the stiff
single-component and multicomponent vesicles are below the center line,
and this results in a clockwise tank-treading behavior. In contrast, the
majority of the membrane of the floppy single-component vesicle is above
the center line, and the result is counterclockwise 
\textcolor{blue}{
rotation, but, again, large normal defomrations are occuring along with
the rotation.
%}
%tank-treading. 
%\textcolor{blue}{
Finally, the stiff single-component vesicle tank treads faster than the
multicomponent cases since more of its membrane is located below the
center line.
}
%In addition, the tank-treading velocity can be correlated to the
%percentage of its membrane that is below the center line. 
%We note, however, that the floppy single-component vesicle is still
%undergoing deformations, so the tangential velocities have not converged
%to a fixed value.
